Assessing Material Inventory Uncertainties in Integrated Fuel Cycle Simulations

### 2018-07-23 paper.tex
formulation

A set of 199 simulations was performed in which all five parameters in Table
\ref{tab:package_uncertainty} are randomly varied. Additionnaly, for each of the
parameters, a set of 199 simulations was performed with only that parameter
being randomly varied using the \gls{OFAT} method to estimated each parameter
contribution to the overall uncertianty.  A reference simulation was performed
with all five parameters fixed at the mean value.

@@

The relative uncertainty of the total uranium consumption starts at about
$7\%$, slowly droping and stabilizing around $3\%$ around year 100.

>>>>

A set of 199 simulations was performed in which all five parameters in Table
\ref{tab:package_uncertainty} are randomly varied. Additionnaly, for each of
those parameters, a set of 199 simulations was performed with only that
parameter being randomly varied, using the \gls{OFAT} method to estimated each
parameter contribution to the overall uncertianty.  A reference simulation was
performed with all five parameters fixed at the mean value.

@@

The relative uncertainty of the uranium consumption dedicated to \gls{PWR}
\gls{UOX} fuel fabrication starts at about $7\%$, slowly dropping from year 20
to 100 and stabilizing around $3\%$ after year 100.
